Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-11-09 awipev-CO2_PAR_sal.Rmd
impossible to make Dygraph

```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
 d_all<- d_all %>%
  dplyr::mutate(
    datetime =ymd_hms(datetime))

sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)

 sal_xts<- sal_xts %>% 
  dplyr::mutate(sal_insitu_ctd_1m = case_when(
    is.na(sal_insitu_ctd_1m) ~ 0,
    TRUE~ sal_insitu_ctd_1m))

sal_xts <- as.xts(sal_xts, order.by = as.Date(d_all$datetime))
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#xts + dygraph
sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
#, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)

 # sal_xts<- sal_xts %>% 
 #  dplyr::mutate(sal_insitu_ctd_1m = case_when(
 #    is.na(sal_insitu_ctd_1m) ~ 0,
 #    TRUE~ sal_insitu_ctd_1m))

sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
